### 2020-03-29 Draft/draft.tex
some typing
add some syntactic typing rule

\newcommand{\true}{\texttt{true}}
\newcommand{\false}{\texttt{false}}
\newcommand{\cref}{\texttt{ref}}
\newcommand{\cfork}[1]{\texttt{fork}\{#1\}}
\newcommand{\cloop}[1]{\texttt{loop}_{#1}\,}
\newcommand{\cbreak}{\texttt{break}\,}
\newcommand{\ccontinue}{\texttt{continue}}
\newcommand{\cif}{\texttt{if}\,}
\newcommand{\cthen}{\,\texttt{then}\,}
\newcommand{\celse}{\,\texttt{else}\,}
\newcommand{\cseq}{\,;;\,}
\newcommand{\creturn}{\texttt{return}\,}

@@

@@

>>>>

\newcommand{\true}{\texttt{true}}
\newcommand{\false}{\texttt{false}}
\newcommand{\cref}{\texttt{ref}}
\newcommand{\cfork}[1]{\texttt{fork}\{#1\}}
\newcommand{\cloop}[1]{\texttt{loop}_{#1}\,}
\newcommand{\cbreak}{\texttt{break}\,}
\newcommand{\ccontinue}{\texttt{continue}}
\newcommand{\cif}{\texttt{if}\,}
\newcommand{\cthen}{\,\texttt{then}\,}
\newcommand{\celse}{\,\texttt{else}\,}
\newcommand{\cseq}{\,;;\,}
\newcommand{\creturn}{\texttt{return}\,}
\newcommand{\ccall}{\texttt{call}\,}

\newcommand{\tunit}{\texttt{unit}}
\newcommand{\tint}{\texttt{int}}
\newcommand{\tbool}{\texttt{bool}}
\newcommand{\vtype}[1]{\textbf{V}[#1]}

@@

The adequacy theorem will have some problem w.r.t the \creturn statement.

@@

Return conditions should be merged with normal conditions upon calling the function.

\paragraph{Typing}

$$
A, B \in \textit{Type} ::= \epsilon \sep \tunit \sep \tint \sep \tbool \sep A \rightarrow B \sep \cdots
$$

\subparagraph{Syntactic Typing}

$$
    \Gamma \vdash e: A_N, A_B, A_C, A_R
$$

\begin{mathpar}
    \inferrule*[left=type-break]{
        \Gamma \vdash e: A_N, A_B, A_C, A_R
    }{
        \Gamma \vdash \cbreak e: \epsilon, A_N + A_B, A_C, A_R
    }
    \and
    \inferrule*[left=type-continue]{}{
        \Gamma \vdash \ccontinue: \epsilon, \epsilon, \tunit, \epsilon
    }
    \and
    \inferrule*[left=type-return]{
        \Gamma \vdash e: A_N, A_B, A_C, A_R
    }{
        \Gamma \vdash \creturn e: \epsilon, A_B, A_C, A_N + A_R
    }
    \and
    \inferrule*[left=type-loop]{
        \Gamma \vdash e: \tunit, A_B, \tunit, A_R
    }{
        \Gamma \vdash \cloop{e} e: A_B, \epsilon, \epsilon, A_R
    }
    \and
    \inferrule*[left=type-apply]{
        \Gamma \vdash e_1: A_N \rightarrow (A_N', A_B', A_C', A_R') \and
        \Gamma \vdash e_2: A_N, A_B, A_C, A_R
    }{
        \Gamma \vdash e_1(e_2): A_N', A_B + A_B', A_C + A_C', A_R + A_R'
    }
\end{mathpar}

where

$$
\begin{aligned}
    A + B &\triangleq \begin{cases}
        A & \text{if } B = \epsilon \text{ or } A = B \\
        B & \text{if } A = \epsilon \text{ or } A = B \\
        \text{undefined} & \text{otherwise}
    \end{cases} \\
    A \rightarrow (B_1, B_2, \cdots) &\triangleq A \rightarrow B_1, A \rightarrow B_2, \cdots
\end{aligned}
$$

\subparagraph{Semantic Typing}

$$
\Gamma \vDash e: A_N, A_B, A_C, A_R \triangleq \Gamma \vDash \htriple{\text{True}}{e}{\vtype{A_N}}{\vtype{A_B}}{\vtype{A_C}}{\vtype{A_R}}
$$
